---
title: "Title"
subtitle: "Subtitle"
author: "John Doe"
institute: "Service XXX, OFB DR XXX"
date: last-modified
format:
  quarto-theme-ofb-revealjs: default
engine: knitr
execute:
  echo: true
  message: false
  warning: false
---

## Color scheme

- Say it with colours → [bleu]{.blue} ; [vert]{.green} ; [marron]{.brown} ; [rouge]{.red} ; [orange]{.orange}



. . .


### Lists

::: {.incremental .highlight-last}
**Bullet list:**

- thing 1
- thing 2
:::

:::: {.fragment}

**Ordered list:**

1. thing 1
1. thing 2

::::

## Code

```{r}
#| echo: true
#| code-line-numbers: false

library(dplyr)
starwars %>% 
  mutate(name, bmi = mass / ((height / 100)  ^ 2)) %>%
  select(name:mass, bmi)
```

## Code with dataframe output

```{r}
#| echo: false
#| code-line-numbers: false
#| 
DT::datatable(
  head(iris, 100), 
  fillContainer = F, 
  rownames = FALSE
)
```

## Leaflet map

<br>

```{r}
#| echo: false
#| fig.width: 8
library(leaflet)

content <- paste(sep = "<br/>",
  "<b><a href='https://www.ofb.gouv.fr/normandie'>OFB DR Normandie</a></b>",
  "Where I am !"
)

leaflet() %>% addTiles(options = providerTileOptions(minZoom=15, maxZoom=18)) %>%
  addPopups(-0.681293,49.038357, content,
    options = popupOptions(closeButton = FALSE)
  )
```

## Block quotes

> Dorothy followed her through many of the beautiful rooms in her
> castle.

## Callouts

:::{.callout-note}
A note
:::

:::{.callout-warning}
A warning
:::

:::{.callout-important}
Something important
:::

:::{.callout-tip}
This is a good idea
:::

## Merci de votre attention {.theme-slide-end}

Slides made with [quarto](https://quarto.org/) and `r fontawesome::fa("r-project", fill = "steelblue")`.